SunPy - Python for Solar Physics

### 2014-01-09 Sunpy_paper_0.4.tex
Add some introduction

\begin{abstract}
This paper presents version 0.4 of SunPy a community developed Python package.
SunPy provides core datatypes and functionality for the processing, analysis and display of solar observational data.

@@

\section{Introduction}

@@

\section{Solar Data Retrieval}

@@

>>>>

\begin{abstract}
This paper presents version 0.4 of SunPy a community developed Python package 
for solar physics.

@@

\section{Introduction}
SunPy is a project dedicated to providing the tools to process and analyse 
solar data in Python.
The Python programming language has gained much traction as a scientific 
programming language in the last decade.
Projects such as \texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib} provide 
the core tools 
needed 
for 
scientific analsysis and visualisation, while other packages such as pandas, 
Astropy or scikit-image provide more domain specific functionality.
SunPy aims to provide such domain specific functionality to the solar physics 
community.

The goal of SunPy is to provide a clean, simple to use and well structured 
package that provides the \textit{core} tools for solar physics.
The primary focus of SunPy's development is current providing specialised, 
linked, datatypes that allow the import, processing and visualisation of solar 
data. Currently the datatypes implemented are \texttt{Map}, \texttt{LightCurve} 
and \texttt{Spectrum}, LLthese cover spatial, timeseries and spectral data 
respectively.

In this paper we will provide an overview of the current functionality of the 
\texttt{sunpy} library as well as giving details on the development model and 
community aspects of the SunPy project.

@@

\section{Solar Data Search and Retrieval}

@@

	\subsection{The SunPy Database}
